---
title: "Ch. 3 Exercises"
subtitle: "Workflow: basics"
author: "Joshua J. Cook, M.S."
date: "today"
format: html
embed-resources: true
editor: visual
toc: TRUE
number-sections: FALSE
colorlinks: TRUE
---

### 1. Why does this code not work?

```{r}
library(tidyverse)
my_variable <- 10
#my_varıable #The i is not an i!
```

### 2. Tweak each of the following R commands so that they run correctly:

```{r}
# libary(todyverse)

# ggplot(dTA = mpg) + 
#   geom_point(maping = aes(x = displ y = hwy)) +
#   geom_smooth(method = "lm)
```

```{r}
library(tidyverse) #grammatical errors

ggplot(data=mpg, mapping=aes(x=displ, y=hwy)) + #apply the mapping globally to simplify code
  geom_point() +
  geom_smooth(method="lm") #syntax error
```

### 3. Press Option + Shift + K / Alt + Shift + K. What happens? How can you get to the same place using the menus?

These are shortcuts in RStudio that display the keyboard shortcuts and save a file. These can be found in the "Tools" and "File" menus respectively.

### 4. Let's revisit an exercise from the [Section 2.6](https://r4ds.hadley.nz/data-visualize.html#sec-ggsave). Run the following lines of code. Which of the two plots is saved as `mpg-plot.png`? Why?

```{r}
my_bar_plot <- ggplot(mpg, aes(x = class)) +
  geom_bar()

my_scatter_plot <- ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()

ggsave(filename = "mpg-plot.png", plot = my_bar_plot) #although not run last, the bar plot is saved because it is explicitly listed as an argument in the ggsave() function. By default, this would have saved the scatter plot. 
```
